Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-10-29 WSSSPE3/report/wg_appendix_software_credit.tex
software credit typo

The discussion then evolved into philosophical questions about the importantance or reliance of a particular work on prior science, materials, or software---in other words, is there a difference between depending on prior scientific advances and depending on particular software (or experimental equipment)?
Multiple contributors converged on the conclusion that unique capabilities require some additional credit.
The---albeit limited---consensus was that if a particular study relied on the unique capabilities of software, data, or an experimental apparatus, then the authors or developers that created this capability should be credited somehow.

>>>>

The discussion then evolved into philosophical questions about the importance or reliance of a particular work on prior science, materials, or software---in other words, is there a difference between depending on prior scientific advances and depending on particular software (or experimental equipment)?
Multiple contributors converged on the conclusion that unique capabilities require some additional credit.
The---albeit limited---consensus was that if a particular study relied on the unique capabilities of software, data, or an experimental apparatus, then the authors or developers that created this capability should be credited somehow.
